---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# programets

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

**programets** is an R package for collecting and analyzing academic impact metrics for NIH-funded research projects. It aggregates data from multiple public sources to help researchers, program managers, and evaluators understand how their projects engage with the broader research community over time.

## What Does It Do?

The package provides unified access to:

- **NIH RePORTER** - Project metadata, funding details, and associated publications
- **iCite** - Citation metrics including Relative Citation Ratio (RCR) for PubMed publications
- **GitHub** - Repository metrics (stars, forks, commits, contributors, issues, PRs) for projects tagged with NIH Core Project Numbers
- **Google Analytics** - Web traffic and engagement data for project websites
- **Europe PMC** - Literature search across millions of publications

## Installation

Install the development version from GitHub:

``` r
# install.packages("pak")
pak::pak("nih-cfde/programets")
```

**Requirements:**
- R >= 4.1.0
- For GitHub data: A Personal Access Token is recommended for higher rate limits

## Quick Start

### 1. Query NIH RePORTER for Project Information

Retrieve comprehensive project metadata including publications, funding details, and principal investigators:

```{r reporter_example}
library(programets)

# Get project info for one or more NIH Core Project Numbers
proj_info <- get_core_project_info(c("u24ca289073"))
proj_info |> colnames()
```

Available fields include: project title, abstract, funding amounts, dates, PIs, publications (PMIDs), and more.

### 2. Get GitHub Repository Metrics

If your project repositories are tagged with NIH Core Project Numbers as topics, you can automatically collect engagement metrics:

```{r git_example}
# Fetch GitHub metrics for repos tagged with your project number
df <- get_github_by_topic(c("u24ca289073"))
df |> colnames()
```

Metrics include: stars, watchers, forks, open/closed issues, open/closed PRs, commit count, contributor count, and more.

**Tip:** Tag your GitHub repositories with your NIH Core Project Number (e.g., `u24ca289073`) to enable automatic discovery.

### 3. Get Citation Metrics from iCite

Calculate impact metrics including the Relative Citation Ratio (RCR) for your publications:

```{r icite_example, eval=FALSE}
# Get citation metrics for PubMed IDs
pmids <- c(26001965, 25015380)
citation_data <- icite(pmids)

# View RCR and other metrics
dplyr::select(citation_data, pmid, title, year, 
              relative_citation_ratio, citation_count)
```

### 4. Search Europe PMC for Publications

Query millions of publications with flexible search syntax:

```{r epmc_example, eval=FALSE}
# Search for publications related to CRISPR
crispr_pubs <- epmc_search(query = "crispr", page_limit = 2)

# Search by author
author_pubs <- epmc_search(query = 'AUTH:"Smith J"', page_limit = 1)
```

### 5. Access Google Analytics Data

Retrieve web traffic data for project websites (requires authentication):

```{r ga_example, eval=FALSE}
# Authenticate with Google (first time only)
googleAnalyticsR::ga_auth()

# Get traffic data
traffic <- ga_dataframe(
  property_id = "123456789",
  start_date = "2024-01-01",
  end_date = "2024-12-31",
  metrics = c("activeUsers", "sessions"),
  dimensions = c("date", "country")
)
```

## Authentication

### GitHub
For increased API rate limits, set up a Personal Access Token:

```{r github_token, eval=FALSE}
# Create a token with: usethis::create_github_token()
# Then use it in your calls:
df <- get_github_by_topic(c("u24ca289073"), token = "your_token_here")
```

### Google Analytics
First-time setup requires authentication:

```{r ga_auth, eval=FALSE}
# Opens browser for Google account authorization
googleAnalyticsR::ga_auth()

# For non-interactive use, see DEVELOPER.md for service account setup
```

## Use Cases

- **Impact Reporting**: Generate comprehensive reports combining publication citations, web traffic, and GitHub engagement
- **Trend Analysis**: Track how metrics evolve over time in response to publications, presentations, or events
- **Portfolio Management**: Compare metrics across multiple projects or funding opportunities
- **Compliance**: Document project outputs and community engagement for progress reports

## Documentation

- **Function Reference**: See `?get_core_project_info`, `?icite`, `?get_github_by_topic`, etc.
- **Vignettes**: Browse vignettes for detailed workflows
- **Developer Notes**: See `DEVELOPER.md` for advanced setup (service accounts, encryption)

## Getting Help

- File issues at: https://github.com/nih-cfde/programets/issues
- Review examples in the vignettes
- Check function documentation with `?function_name`

## Authors

- Sean Davis (seandavi@gmail.com)
- David Mayer (david.mayer@cuanschutz.edu)

## License

MIT + file LICENSE

