---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# programets

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of programets is to gather metrics from iCite, Google Analytics, GitHub, and other sources to help assess the impact of your NIH Project on the broader research community. 

## Installation

You can install the development version of programets from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("nih-cfde/programets")
```

## Example Usage

Query the NIH RePORTER:

```{r reporter_example}
library(programets)

proj_info <- get_core_project_info(c("u24ca289073"))
proj_info |> colnames()
```

Tag your GitHub repositories with NIH Core Project Numbers to download common metrics:

```{r git_example}
df <- get_github_by_topic(c("u24ca289073"))
df |> colnames()
```

