---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# programets

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of programets is to compile public metrics from iCite, Google Analytics, GitHub, and related sources to help researchers understand how their NIH project engages with the broader research community. The package is designed to highlight how project impact evolves over time, such as in response to publications or events.

## Installation

You can install the development version of programets from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("nih-cfde/programets")
```

## Example Usage

Query the NIH RePORTER:

```{r reporter_example}
library(programets)

proj_info <- get_core_project_info(c("u24ca289073"))
proj_info |> colnames()
```

Tag your GitHub repositories with NIH Core Project Numbers to download common metrics:

```{r git_example}
df <- get_github_by_topic(c("u24ca289073"))
df |> colnames()
```

